---
title: "Meka McCammon Assignment # 10"
date: 17 April 2020
output: html_notebook
---

This notebook includes the analysis of Johnson Elementary ELA Data for assignment # 10


#### 1. Write a script to import and tidy the Johnson Elementary Project Data
```{r include=FALSE}
library(tidyverse)
library(here)
```
```{r include=FALSE}
# Read in the data, skip the first 4 rows, specify Room as a factor and name the columns
jep <- read_csv(here("Data","Johnson Elementary ELA Project.csv"), skip = 4,
                col_types = cols(Room = col_factor()),
                col_names = c("Room", "ID", "Tardies;Absences","Q1", "Q2", "Q3", "Q4"))
```
```{r include=FALSE}
# next gather the quarters to long format, and label the new columns to refer to quarter and the rating
(gather.quarters <- jep %>%
  gather(`Q1`, `Q2`, `Q3`, `Q4`,
         key = "Quarter",
         value = "Rating"))
```
```{r include=FALSE}
# separate tardies and absences into their own columns
(separate.attendance <- gather.quarters %>%
  separate(`Tardies;Absences`,into = c("Tardies", "Absences"), convert = TRUE))
```
```{r include=FALSE}
# Fill the room number down each section 
(fill.room <- separate.attendance %>% 
  fill(Room))
```
```{r echo=FALSE}
#  remove cells that say NA associated with each Room by ID 
(tidy.jep <- fill.room %>% 
   drop_na(Room:Absences))
# * another way to do this filter(!is.na(ID))
```


#### 2. Obtain summary statistics for the number of tardies and absencnes in each room 

```{r echo=TRUE}
(summary.jep <- tidy.jep %>%
  group_by(Room) %>%
  summarise(tardy.mean = mean(Tardies),tardy.sd = sd(Tardies), 
            tardy.median = median(Tardies), 
            tardy.quantile1 = quantile(Tardies, probs = 0.25, na.rm = TRUE), 
            tardy.quantile3 = quantile(Tardies, probs = 0.75, na.rm = TRUE), 
            absence.mean = mean(Absences),absence.sd = sd(Absences), 
            absence.median = median(Absences), 
            absence.quantile1 = quantile(Absences, probs = 0.25, na.rm = TRUE),
            absence.quantile3 = quantile(Absences, probs = 0.75, na.rm = TRUE)))
```


#### 3. Here are the frequencies of missing data points for each quarter by room 
```{r echo=TRUE}
(missing.quarters <- tidy.jep %>%
  group_by(Room,Quarter) %>%
  count(sum(is.na(Rating))))
```

#### 4. Here is a line graph of the median trends across the fourth quarter by class
```{r echo=TRUE}
median.quarters <- tidy.jep %>%
  group_by(Quarter,Room) %>%
  summarize(quarter.medians = median(Rating, na.rm = TRUE)) %>%
  ggplot(aes(x= Quarter, y = quarter.medians, group = Room)) +
  geom_line(aes(color = Room), show.legend = FALSE) +
  facet_wrap(vars(Room), nrow = 2) +
  labs(x = "Quarter", y = "Median ELA Ratings",
      title = "Johnson Elementary ELA 5th Grade Ratings",
      subtitle = "Ratings Across Four Quarters by Classroom")

median.quarters

  
```
#### 5.Compare carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City to Atlanta. 

```{r include=FALSE}
library(here)
# First filter by year destination and origin

flights <- read_csv(here("Data","NYC Flights 2013.csv")) 
```
```{r echo=TRUE}
flights2013 <- flights %>% 
   filter(year == 2013, dest == "ATL", !is.na(arr_delay)) %>%
   mutate(timely= (arr_delay <=0)) 
```
```{r}
ggplot(data = flights2013, mapping = aes(x=carrier)) +
geom_bar(aes(fill = "timely"), position = "fill")
```
  
