---
title: "Meka McCammon Assignment # 10"
date: 17 April 2020
output: html_notebook
---

This notebook includes the analysis of Johnson Elementary ELA Data for assignment # 10


#### 1. Write a script to import and tidy the Johnson Elementary Project Data
```{r}
library(tidyverse)
library(here)
```


```{r include=FALSE}
jep <- read_csv(here("Data","Johnson Elementary ELA Project.csv"), skip = c(4),
                col_types = cols(X1 = col_factor()),
                col_names = c("Room", "ID", "Tardies;Absences","Q1", "Q2", "Q3", "Q4"))
```
```{r echo=FALSE}
jep <- jep %>%
  separate(`Tardies;Absences`,into = c("Tardies", "Absences"), convert = TRUE)
```
```{r}
jep <- jep %>% fill(Room)
```
```{r}
drop.missing <- jep %>% drop_na(Room:Absences)
```


#### 2. Obtain summary statistics for the number of tardies and absencnes in each room 

```{r echo=FALSE}
summary.jep <- drop.missing %>%
  group_by(Room) %>%
  summarise(tardy.mean = mean(Tardies), tardy.sd = sd(Tardies), tardy.median = median(Tardies),
            absence.mean = mean(Absences), absence.sd = sd(Absences),
            absence.median = median(Absences))
summary.jep
```


#### Here are the frequencies of missing data points for each quarter by room 
```{r}
(missing.quarters <- drop.missing %>%
  group_by(Room) %>%
  summarise(missing.Q1 = sum(is.na(Q1)), missing.Q2 = sum(is.na(Q2)), missing.Q3 = sum(is.na(Q3)),
            missing.Q4 = sum(is.na(Q4))))
```

#### Here is a boxplot of the median trends across the fourth quarter by class
```{r echo=FALSE}


  
```
#### 5. construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City toAtlanta. 

```{r}
library(here)
#First filter by year destination and origin

flights <- read_csv(here("Data","NYC Flights 2013.csv")) 

(twenty.thirteen.flights <- filter(flights, year == 2013, origin == "JFK", dest == "ATL"))
```

```{r}

#Next filter the 2013 flights from NYC to ATL that arrived on time or early 
(on.time.arrival <-(twenty.thirteen.flights %>%
  group_by(carrier) %>%
   filter(arr_delay <= 0)))
```


```{r}
#Next filter the 2013 flights from NYC to ATL that arrived on time 
(late.arrival <-(twenty.thirteen.flights %>%
  group_by(carrier) %>%
   filter(arr_delay > 0)))
```

```{r}

(sum.late <-(twenty.thirteen.flights %>%
  group_by(carrier) %>%
   filter(arr_delay > 0 %>%
   summarize(count = n()))))
```
           

